Mistletoe, Friend and and Foe; Ecosystem implications of mistletoe infection

### 2017-05-24 manuscript/manuscript.Rmd
changed csl to ERL template

---
title: Mistletoe, Friend and and Foe; Ecosystem implications of mistletoe infection 
author: ""
date: ""
output:
  word_document:
  reference_docx: manuscriptstyle.docx
  number_sections: yes
csl: tree-physiology.csl
bibliography: mistletoe.bib
---

>>>>

---
title: Mistletoe, Friend and and Foe; Ecosystem implications of mistletoe infection 
author: ""
date: ""
output:
  word_document:
  reference_doc: test2.docx
  number_sections: yes
csl: environmental-research-letters.csl
bibliography: mistletoe.bib
---
